### 2022-03-04 paper/localpsf.tex
about to try eliminating f_xy(xi) notation

\subsection{Local mean-displacement invariance}

@@

In Section \ref{sec:intro} we noted that the integral kernel, $\Aker$, is inaccessible. Here we describe how we compute approximate kernel entries,
\begin{equation*}
\widetilde{\Phi}(y,x) \approx \Phi(y,x),
\end{equation*}
for arbitrary pairs of points $(y,x) \subset \Omega \times \Omega$ via interpolation.
% while Section \ref{sec:approximate_kernel_entries} we showed how we can cheaply evaluate approximate kernel entries at arbitrary pairs of points $(y,x) \in \Omega \times \Omega$.
To that end, we define the function
\begin{equation}
\label{eq:fxyxp}
f_{y,x}(x') := \frac{V(x)}{V(x')}\phi_{x_i}\left(y - \mu(x) + \mu(x')\right).
\end{equation}
It follows from inspection that 
\begin{equation*}
\Phi(y,x) = f_{y,x}(x),
\end{equation*}
and from the discussion in Section SEC, we expect that $\Phi(y,x) \approx f_{y,x}(x')$ when $x'$ is close to $x$. The factor $\frac{V(x)}{V(x_i)}$, which was not discussed in Section SEC, is a form of preconditioning that improves the quality of this approximation in situations where $V(x)$ varies rapidly. 
%, as is commonly the case for many operators of practical interest. In the Hessian for the Stokes inverse problem, for example, we observe that $V(x)$ varies over six orders of magnitude.
%As discussed in Section SECTION, we make the approximation
%\begin{equation*}
%	\Phi(y,x) = \phi_x(y) \approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right)
%\end{equation*}
%if $x'$ is close to $x$. Hence, w

>>>>

\subsection{Local mean-displacement invariance}
\label{eq:local_mean_displacement_invariance}

@@

%In Section \ref{sec:intro} we noted that computing $\Aker\left(y,x\right)$ is computationally costly. 
This section describes how we compute approximate kernel entries
\begin{equation*}
\widetilde{\Phi}(y,x) \approx \Phi(y,x).
\end{equation*}
%for arbitrary pairs of points $(y,x) \subset \Omega \times \Omega$.
% while Section \ref{sec:approximate_kernel_entries} we showed how we can cheaply evaluate approximate kernel entries at arbitrary pairs of points $(y,x) \in \Omega \times \Omega$.
Let
\begin{equation}
\label{eq:fxyxp}
f_{y,x}(x') := \frac{V(x)}{V(x')}\phi_{x_i}\left(y - \mu(x) + \mu(x')\right).
\end{equation}
It follows from inspection that $\Phi(y,x) = f_{y,x}(x)$,
and from the discussion in Section \ref{eq:local_mean_displacement_invariance}, we expect 
$
\Phi(y,x) \approx f_{y,x}(x')
$
when $x'$ is close to $x$. The factor $\frac{V(x)}{V(x_i)}$, which was not discussed in Section \ref{eq:local_mean_displacement_invariance}, is a form of preconditioning that improves the quality of this approximation in situations where $V(x)$ varies rapidly. 
%, as is commonly the case for many operators of practical interest. In the Hessian for the Stokes inverse problem, for example, we observe that $V(x)$ varies over six orders of magnitude.
%As discussed in Section SECTION, we make the approximation
%\begin{equation*}
%	\Phi(y,x) = \phi_x(y) \approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right)
%\end{equation*}
%if $x'$ is close to $x$. Hence, w
